An Authoritative Adventure

### 2020-12-22 article.tex
Tweaks to the article.tex description of setting full color scheme values

\subsection{More Theme Colors Control}
Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class. This command takes seven (7) |<color>| values that map to the following color variables within the theme:

\begin{DndTable}[header=Complex Theme Parameter Map]{cX}
  \textbf{Param \#} & \textbf{Variable Mapping} \\
  1 & \textit{themecolor}, \textit{tablecolor} \\
  2 & \textit{commentcolor}, \textit{sidebarcolor} \\
  3 & \textit{readaloudcolor} (DndReadAloud background) \\
  4 & \textit{readaloudbordercolor} \\
  5 & \textit{titlecolor} \\
  6 & \textit{titlerulecolor} \\
  7 & \textit{pagecolor} (page numbers and footer) \\
\end{DndTable}

@@

An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook:

>>>>

\subsection{Extra Theme Color Control}
Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class. This command takes seven (7) |<color>| values that map to the following color variables within the theme:

\begin{DndTable}[header=Complex Theme Parameter Map]{clX}
  \textbf{\#} & \textbf{Variable Set} & \textbf{Affected Style} \\
  1 & \textit{themecolor} & Used in |DndSetThemeColor|, set for future compatibility \\
    & \textit{tablecolor} & |DndTable| \\
  2 & \textit{commentcolor} & |DndComment| \\
    & \textit{sidebarcolor} & |DndSidebar| \\
  3 & \textit{readaloudcolor} & |DndReadAloud| background \\
  4 & \textit{readaloudbordercolor} & |DndReadAloud| border \\
  5 & \textit{titlecolor} & Titles of sections (|section|, |subsection|, etc) \\
  6 & \textit{titlerulecolor} & |subsection| title ruling \\
  7 & \textit{pagecolor} & Page numbers and footer \\
\end{DndTable}

@@

An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook. Note that the values for \textit{titlered} and \textit{titlegold} are used for the title and title rule colours unchanged in this example.
